msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-13 paper.tex
Add dependent packages from GitHub

The more recent trend has been to move away from this file and command-line
driven approach and to instead provide direct interfaces to the simulation
engines via an Application Programming Interface (API)~\citep[e.g.][]{
thornton2014cpp,kelleher2016efficient,becheler2019quetzal,haller2019slim}. This
approach greatly increases the flexibility of simulations, and allows all
processing for many simulation analyses to be performed in a single script. The
primary interface for \msprime\ is through a well documented and stable Python
API, which has allowed a number of downstream tools to be built on
% JK: must be more, right?
top of it~\citep{adrion2020community,rivera2021simulation}
as well as numerous easily reproducible simulation
% TODO: more papers with exemplorary reproducible simulation pipelines based
% on msprime!
pipelines~\citep[e.g.][]{martin2017human}.
We also provide an \ms\ compatible
command line interface to support existing workflows, as well as the
\texttt{msp simulate} command that supports specifying demographic models in
Demes format~\citep{gower2021demes}.

>>>>

The more recent trend has been to move away from this file and command-line
driven approach and to instead provide direct interfaces to the simulation
engines via an Application Programming Interface (API)~\citep[e.g.][]{
thornton2014cpp,kelleher2016efficient,becheler2019quetzal,haller2019slim}. This
approach greatly increases the flexibility of simulations, and allows all
processing for many simulation analyses to be performed in a single script. The
primary interface for \msprime\ is through a well documented and stable Python
API, which has allowed a number of downstream tools to be built on
top of
% Found these through the Dependent packages on GitHub
it~\citep{kamm2020efficiently,adrion2020predicting,adrion2020community,
rivera2021simulation,de2021geonomics}
as well as numerous easily reproducible simulation
% TODO: more papers with exemplorary reproducible simulation pipelines based
% on msprime!
pipelines~\citep[e.g.][]{martin2017human}.
We also provide an \ms\ compatible
command line interface to support existing workflows, as well as the
\texttt{msp simulate} command that supports specifying demographic models in
Demes format~\citep{gower2021demes}.
